%!TeX root=indexUIB.tex

\chapter{Abstract}
Attitude sensors are more and more widely used and their price is decreasing. We can find them in many electronic systems designed for specific purposes. Some examples are in wearable devices, navigation or control systems. We can use some of the devices for covering new use cases and developing new systems. I still didn't find any device that fulfills all my requirements for developing new data processing algorithms.

I have developed a new wearable independent device for capturing and processing the measured data. The independence means no external wires and no external power supply here. The device is able to work outdoors, to log the measured data and to provide a direct output based on internal computations. The user can choose between completely wireless communication or wired connection to other electronics. The sensors measure inertial, attitude, position and atmospheric values.

For outdoor testing of the device, I selected a task about movement analysis of a horse. The devices were placed on the horse's body as wearable devices and I was developing algorithms for determination of the type of its movement -- stand, walk, trot or gallop. The algorithm first determines very basic types of movements and then it's looking for more advanced ones based on previous results. The types of movement are defined as statements, so new types of movement of any subject can be detected without modification of the computation code.

In general, the developed device can be used for sensor data capturing, onboard data processing, navigation or control of moving mechanics. The device works independently, so it is easy to install on the measured subjects.
