\chapter{Conclusion}
The thesis was finally split into four milestones. The first milestone was achieved when I have decided to develop a new data logging hardware because the existing solutions did not fulfill all the requirements. I have successfully developed the SensorBoard hardware in the second step, and then the board was manufactured in six copies. I have achieved the second milestone with the manufactured hardware. The third phase was about testing the device and about implementing libraries for communication between the controller and other parts, mainly sensors. I have found several mistakes in the hardware design during programming, but all of them were corrected. The third milestone was achieved when I had working hardware with C++ libraries for easier communication with sensors and other parts of the device. These libraries are a part of the API. During the last phase, I have implemented the firmware for real-time movement analysis. When the SensorBoard is placed on a horse under the saddle, it is able to recognize the kind of horse movement. This firmware demonstrates the functionality of the designed hardware in real use. I have achieved the last milestone during the first successful test of the platform on a horse's body.

There are many applications and use cases of the SensorBoard presented as examples in the thesis. I have selected the movement analysis case because this task started the whole project in the beginning. The movement analysis firmware shows the advantages of running some user code on the hardware. We can see the results of the analysis in real-time.

If there is an interest in future work with this hardware, I would like to recommend to create the second version of the SensorBoard with attention to the list of hardware errors presented in this thesis. The actual version was designed as a prototype and it is not recommended for production. The prototype of the SensorBoard was used, for example, as a simple autopilot of a small quadcopter, I believe it will be used in several applications in the near future. I hope that the firmware for the movement analysis of a horse will help to work with this kind of animals easier.
