%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% I, the copyright holder of this work, release this work into the
%% public domain. This applies worldwide. In some countries this may
%% not be legally possible; if so: I grant anyone the right to use
%% this work for any purpose, without any conditions, unless such
%% conditions are required by law.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[
  printed, %% This option enables the default options for the
           %% digital version of a document. Replace with `printed`
           %% to enable the default options for the printed version
           %% of a document.
  table,   %% Causes the coloring of tables. Replace with `notable`
           %% to restore plain tables.
  lof,     %% Prints the List of Figures. Replace with `nolof` to
           %% hide the List of Figures.
  lot,     %% Prints the List of Tables. Replace with `nolot` to
           %% hide the List of Tables.
  %% More options are listed in the user guide at
  %% <http://mirrors.ctan.org/macros/latex/contrib/fithesis/guide/mu/fi.pdf>.
]{fithesis3}

\usepackage[
  main=english,  %% By using `czech` or `slovak` as the main locale
                 %% instead of `english`, you can typeset the thesis
                 %% in either Czech or Slovak, respectively.
  english, czech %% The additional keys allow
]{babel}         %% foreign texts to be typeset as follows:

%% The following section sets up the metadata of the thesis.
\thesissetup{
%    date          = \the\year/\the\month/\the\day,
    date          = 2018/05/01,
    university    = mu,
    faculty       = fi,
    type          = mgr,
    author        = Bc. Bedřich Said,
    gender        = m,
    advisor       = {RNDr. Zdeněk Matěj, Ph.D.},
    title         = {Device for Analysis of Movement Using Inertial Sensors},
    TeXtitle      = {Device for Analysis of~Movement Using~Inertial~Sensors},
    keywords      = {Electronic Device, Printed Circuit Board, Inertial Sensors, Inertial Measurement Unit, Internet of Things, Movement Analysis, Horse},
    TeXkeywords   = {Electronic Device, Printed Circuit Board, Inertial Sensors, Inertial Measurement Unit, Internet of Things, Movement Analysis, Horse},
    bib           = bibliography.bib,
}

\thesislong{thanks}{
I wish to express my sincere thanks to \begin{otherlanguage}{czech}RNDr. Zdeněk Matěj, Ph.D.\end{otherlanguage}, my advisor, for his continuous support and answering my questions. I am also grateful to \begin{otherlanguage}{czech}Robotárna in Brno \end{otherlanguage} for providing me with some necessary facilities for the research. Special thanks go to \begin{otherlanguage}{czech}Bc. Alena Bečková \end{otherlanguage} and other horse riders with their horses for continuous support during measurements and analyses. I would like to thank to \begin{otherlanguage}{czech}Monet+ \end{otherlanguage} company, which was a~commercial partner for this research.
}

\thesislong{abstract}{
Currently, the inertial sensors are more widely used, and their price is decreasing. The lower price allows creating new solutions with lower costs. Some examples can be found in wearable devices, mobile phones, navigation or control systems. There are several devices for various use cases on the market.

These devices usually cover their use cases and do not have any additional features like power independence, enough logging memory or openness for user code. The remaining hardware that fulfills all the conditions above is usually expensive.

I have developed a~new wearable independent device for capturing and processing the measured data. The independence means no external wires and no external power supply here. The device is able to work outdoors, to log the measured data and to provide a~direct output based on internal computations. The user can choose between completely wireless communication or wired connection to other electronics. The sensors measure inertial, attitude, position and atmospheric values.

For outdoor testing of the device I have selected the task about movement analysis of a~horse. I placed the devices on the horse's body as wearable devices and I was developing algorithms for determination of the basic types of its movement -- stand, walk, trot, canter or gallop.

In general, the developed device can be used for capturing data from sensors, onboard data processing, navigation or control of moving mechanics. The electronics work independently, so it is easy to install it on the measured or controlled objects.
}

\usepackage{makeidx}      %% The `makeidx` package contains
\makeindex                %% helper commands for index typesetting.

%% These additional packages are used within the document:
\usepackage{paralist} %% Compact list environments
\usepackage{amsmath}  %% Mathematics
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}      %% Hyperlinks
\usepackage{listings} %% Source code highlighting
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hhline}
\usepackage{siunitx}
\usepackage[most]{tcolorbox}
\usepackage{geometry}
\usepackage{framed}
\usepackage{adjustbox}
\usepackage{tcolorbox}
\usepackage[nottoc]{tocbibind}
\usepackage{soul}
\usepackage{multirow, tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{gensymb}
\usepackage{multicol}
\usepackage{caption}
\usepackage[acronym,nomain]{glossaries}  %% Load the package with the acronym option
\loadglsentries[\acronymtype]{Acronyms}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}
\newtheorem*{remark}{Remark}

%% Special colors definitions
\definecolor{background}{HTML}{F5DD9D}
\definecolor{symbolColorTop}{HTML}{FFECB3}
\definecolor{symbolColorBox}{HTML}{FFF9E5}
\definecolor{gray}{rgb}{0.25,0.25,0.25}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}
\definecolor{lightblue}{rgb}{0.9,0.95,1.0}
\definecolor{darkgreen}{rgb}{0.0,0.6,0.0}
\definecolor{brown}{HTML}{A52A2A}
\definecolor{darkmagenta}{HTML}{8B008B}

\lstset{
  basicstyle      = \ttfamily,%
  identifierstyle = \color{black},%
  keywordstyle    = \color{blue},%
  keywordstyle    = {[2]\color{cyan}},%
  keywordstyle    = {[3]\color{olive}},%
  stringstyle     = \color{teal},%
  commentstyle    = \itshape\color{magenta}}
\usepackage{floatrow} %% Putting captions above tables
\floatsetup[table]{capposition=top}

\newcommand\Cpp{
	\lstset{
		basicstyle=\ttfamily,
		columns=fullflexible,
		showstringspaces=false,
		tabsize=4,
		numbers=left,
		xleftmargin=2em,
		backgroundcolor = \color{lightblue},
		language=C++,
		identifierstyle=\color{brown},
		keywordstyle=\color{blue},
		stringstyle=\color{red},
		commentstyle=\color{darkgreen},
		morecomment=[l][\color{darkmagenta}]{\#}
	}
}

%% Definition of the box with declarations of used symbols.
\newcommand\highlightedBox[2]{
	\tcbset{
		enhanced,
		colback=symbolColorBox,
		boxrule=1.0pt,
		colframe=symbolColorTop!80!black,
		coltitle=black,
		fonttitle=\bfseries
	}
	\vspace{0.5cm}
	\begin{tcolorbox}[title=#1:,lifted shadow={0mm}{0mm}{0mm}{0.1mm}{black!50!white}]
		#2
	\end{tcolorbox}
	\vspace{0.5cm}
}

\newcommand\itwoc[0]{
	I$^{2}$C
}

\setlength{\arrayrulewidth}{1pt}

% Definition used colors
\newcommand\greenLow[0]{\cellcolor{green!25} Low}
\newcommand\greenSpare[0]{\cellcolor{green!25} Spare}
\newcommand\yellowMedium[0]{\cellcolor{yellow!25} Medium}
\newcommand\redHigh[0]{\cellcolor{red!25} High}

\newcommand\greenYes[0]{\cellcolor{green!25} Yes}
\newcommand\redNo[0]{\cellcolor{red!25} No}

\newcommand\greenCell[1]{\cellcolor{green!25} #1}
\newcommand\yellowCell[1]{\cellcolor{yellow!25} #1}
\newcommand\redCell[1]{\cellcolor{red!25} #1}

\newcommand\ac[1]{\index{#1}\gls{#1}}
\newcommand\ind[1]{#1\index{#1}}

% Generate the glossary
\makeglossaries
\glstoctrue

\begin{document}
\newgeometry{twoside, top=2.5cm, left=3cm, textwidth=16cm, textheight=24cm}

\tcbset{tab2/.style={enhanced,fonttitle=\bfseries,fontupper=\normalsize\sffamily, colback=yellow!10!white, colframe=black, colbacktitle=white, coltitle=black, center title}}

\include{Introduction}

\include{Hardware}

\include{Software}

\include{Analysis}

\include{Conclusion}

% Acronym definitions
\include{Acronyms}
%Print the glossary
\printglossary[type=\acronymtype, title=Used Acronyms, toctitle=Used Acronyms]

\printbibliography[heading=bibintoc] %% Print the bibliography.

\makeatletter\thesis@blocks@clear\makeatother
\phantomsection
\printindex

\appendix
\include{Appendix}

\end{document}
